Automated Topic Naming

### 2011-09-02 ese/ese.tex
fixed missing ref error

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero, one, or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement
in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can only map topics to a single class. 
The Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank
% multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

Table \ref{tab:iterr} describes the Cohen Kappa and the Spearman
correlation of our per topic annotations for each tag. We had to
evaluate inter-rater reliability this way because 1 topic could be
tagged with more than 1 annotation.

>>>>

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero, one, or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement
in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can only map topics to a single class. 
tab:iterrThe Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank
% multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

Table \ref{tab:interr} describes the Cohen Kappa and the Spearman
correlation of our per topic annotations for each tag. We had to
evaluate inter-rater reliability this way because 1 topic could be
tagged with more than 1 annotation.
